Assessing Replication via P-values

### 2018-07-12 McNemar's Test/draft_mcnemars_ttest.Rmd
Sentence change about variance of 4/n

Like McNemar's test, the power of the t-test to detect if the \textit{p}-values of the original studies are different from those of the replication studies depends upon the power of both the original and replication studies. Consider a single study (either original or replication), with the null hypothesis $H_0:\theta_i = 0$. The finding from this study is significant if $\frac{|T_{i}|}{\sqrt{v_i}} \geq 1.96$ which is equivalent to $p_i \leq 0.05$ since $p_i = \Phi^{-1} \Big ( \frac{|T_i|}{\sqrt{v_i}} \Big)$ where $\Phi^{-1}$ is the standard normal quantile function. Assuming that the variance is known for such a study which is a function of the sample size $n_i$, then the power to detect if $\theta_i$ is statistically different from 0 depends on the estimate $T_i$ and the sample size $n_i$. Extending this to the test statistic for the t-test, we note that the mean of the paired difference of \textit{p}-values can be written as

>>>>

Like McNemar's test, the power of the t-test to detect if the \textit{p}-values of the original studies are different from those of the replication studies depends upon the power of both the original and replication studies. Consider a single study (either original or replication), with the null hypothesis $H_0:\theta_i = 0$. The finding from this study is significant if $\frac{|T_{i}|}{\sqrt{v_i}} \geq 1.96$ which is equivalent to $p_i \leq 0.05$ since $p_i = \Phi^{-1} \Big ( \frac{|T_i|}{\sqrt{v_i}} \Big)$ where $\Phi^{-1}$ is the standard normal quantile function. Assuming that for each group $\sigma_i^2=1$, then since they are coming from paired data of equal size the variance for each $v_i$ is $\frac{4\sigma^2}{n}$ thus making $v_i = \frac{4}{n}$. Then the power to detect if $\theta_i$ is statistically different from 0 depends on the estimate $T_i$ and the sample size $n_i$. Extending this to the test statistic for the t-test, we note that the mean of the paired difference of \textit{p}-values can be written as
